Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-25 manuscript/manuscript.tex
Fixed typo

\citet{Uieda2016} developed a forward gravitational model based on 
tesseroids with homogeneous densities using the GLQ approximation 
method.
The main issue of the GLQ is that the approximation becomes less 
accurate when the computation point is closer to the tesseroid of for 
smaler GLQ order \citep{Ku1977}.
Although the model developed by \citet{Uieda2016} uses a second order GLQ, it 
ensures the accuracy implementing a modified version of the adaptive 
discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain 
distance-size ratio is lower than a predefined value ($D$) that controls the 
accuracy of the computation.
\citet{Uieda2016} have also objectively obtained standard values of $D$ 
for gravitational potential, gradients and tensor components comparing 
the numerical model with the fields generated by a spherical shell, 
which constitutes a special case of the volume integrals that has 
analytical solution \citep{LaFehr1991, Mikuska2006, Grombein2013} 
\todo[inline]{citar mas??}.

>>>>

\citet{Uieda2016} developed a forward gravitational model based on 
tesseroids with homogeneous densities using the GLQ approximation 
method.
The main issue of the GLQ is that the approximation becomes less 
accurate when the computation point is closer to the tesseroid or for 
smaler GLQ order \citep{Ku1977}.
Although the model developed by \citet{Uieda2016} uses a second order GLQ, it 
ensures the accuracy implementing a modified version of the adaptive 
discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain 
distance-size ratio is lower than a predefined value ($D$) that controls the 
accuracy of the computation.
\citet{Uieda2016} have also objectively obtained standard values of $D$ 
for gravitational potential, gradients and tensor components comparing 
the numerical model with the fields generated by a spherical shell, 
which constitutes a special case of the volume integrals that has 
analytical solution \citep{LaFehr1991, Mikuska2006, Grombein2013} 
\todo[inline]{citar mas??}.
